Hydra Battles and Cie

### 2021-03-06 doc/chapter-primrec.tex
new exercise
minor corrections

\index{primrec}{Exercises}
\begin{exercise}
Prove the following lemmas (which may help to solve thenext  exercise).

@@

\section{Proving that a given function is \emph{not} primitive recursive}

@@

We preferred to use the former definition, in order to
take advantage from generic lemmas about \texttt{iterate}.

@@

>>>>

\index{primrec}{Exercises}
\begin{exercise}
Prove the following lemmas (which may help to solve the next  exercise).

@@

\section{Proving that a given function is \emph{not} primitive recursive}
\label{sect:ack-not-PR}

@@

We prefered to use the former definition, in order to
take advantage from generic lemmas about \texttt{iterate}.

@@

\begin{remark}
It is easy to prove that any unary function which dominatates \texttt{fun n => Ack n n} fails to be primitive recursive. We use an instance on \texttt{majorAnyPR} for unary functions.
\vspace{4pt}
\noindent

\emph{From \href{../theories/html/hydras.MoreAck.AckNotPR.html}{MoreAck.AckNotPR}}.
\begin{Coqsrc}
Lemma majorPR1  (f: naryFunc 1)(Hf : isPR 1 f)
  : exists (n:nat), forall x ,  f x  <= Ack n x.
(* ... *)
\end{Coqsrc}

Then, we write  a short proof by contradiction.

\begin{Coqsrc}
Section dom_AckNotPR.

  Variable f : nat -> nat.
  Hypothesis Hf : dominates f (fun n => Ack n n).

 Lemma dom_AckNotPR: isPR 1 f -> False.
  Proof.
    intros H;  destruct Hf as [N HN].
    destruct  (majorPR1 _ H) as [M HM].
    pose (X := Max.max N M).
    specialize (HN X  (Max.le_max_l N M)).
    specialize (HM X);
      assert (Ack M X <= Ack X X) by (apply Ack_mono_l; subst; lia).
    lia.
  Qed.

End dom_AckNotPR.
\end{Coqsrc}
\end{remark}
